Manuscript

### 2025-03-27 Manuscript_MD_ScoreReLiability.qmd
fix inconsistent issue by more bootstrap

@tbl-R1R2 reports the meta-analytic estimates of observed and true score
variances, including their heterogeneity and metrics $R_1$ and $R_2$
across all 12 phenomena. In @tbl-R1R2 we see that for ten out of 12
phenomena, the $R_2$ metric is larger than the $R_1$ metric.
Additionally, we observe that across nine phenomena, $R_2$ is larger
than .96. This implies that of the heterogeneity observed in score
variances, 97% or more could not be explained by differences in random
error introduced by the measuring instrument, but by genuine differences
in the underlying distribution.

For one of the phenomena, however, we observe a large disparity compared
to the rest of the results. For the Shnabel_Willingness_Reconcile_RPP
phenomenon, $R_2$ is very low, below .25. This makes it lower than its
$R_1^3 = .574$. This would imply that for this phenomenon, the
conditions for a reduction in ES heterogeneity would be met. However, in
@tbl-tauES, we find no such reduction. What becomes apparent, however,
is that for this phenomenon we are working with the low number of 9
administration sites. Estimation precision for heterogeneity in variance
components, even more so than for ES, largely depends on the sample
size. In Beinhauer et al. (ref) we come to the conclusion that at 10
items, which the Willingness to Reconcile scale consists of, a sample
size around 33 is required to achieve sufficient power for a statistical
test of score variance heterogeneity. Most likely, the low sample size
led to implausible estimates in both true and total score variance
heterogeneity and subsequently to an implausible estimate of $R_2$.
Meta-analytic estimates, especially those concerning score variance
components such as $R_2$, therefore should be interpreted with caution,
if the sample size was particularly low.

Similarly, for the two exceptional phenomena where the attenuation
correction procedure actually led to an increase in ES heterogeneity
(Srull_Behavior_Hostility and Shnabel_Willingness_Reconcile_RPP), the
significance test for the ES heterogeneity was not significant, both
before and after the correction. The results regarding $R_2$ indicate
that the majority of score variance heterogeneity was due to differences
in true score variance $\sigma^2_T$. Both phenomena were examined using
a rather low number of administration sites (22 and 9 respectively),
implying that issues of estimation precision might explain the
inconclusive results. Lastly, for one out of the 12 phenomena, the
Albarracin_Priming_SAT phenomenon, we find a $\tau_{\sigma^2_X}$ of 0.
Therefore, the $R_2$ metric could not be computed, as the denominator
would have been zero. However, we also did not identify statistically
significant ES heterogeneity in the first place. This phenomenon was
assessed with a particularly low number of replications (8). As
discussed, adequate power to detect heterogeneity in score reliability
and observed score variance requires a larger number of replications
than adequate power to detect heterogeneity.

>>>>

@tbl-R1R2 reports the meta-analytic estimates of observed and true score
variances, including their heterogeneity and metrics $R_1$ and $R_2$
across all 12 phenomena. In @tbl-R1R2 we see that for ten out of 12
phenomena, the $R_2$ metric is larger than the $R_1$ metric.
Additionally, we observe that across eight phenomena, $R_2$ is larger
than .96. This implies that of the heterogeneity observed in score
variances, 97% or more could not be explained by differences in random
error introduced by the measuring instrument, but by genuine differences
in the underlying distribution.

For the two exceptional phenomena where the attenuation correction
procedure actually led to an increase in ES heterogeneity
(Srull_Behavior_Hostility and Shnabel_Willingness_Reconcile_RPP), the
significance test for the ES heterogeneity was not significant, both
before and after the correction. The results regarding $R_2$ indicate
that the majority of score variance heterogeneity was due to differences
in true score variance $\sigma^2_T$. Since either the heterogeneity was
so small or the sample size so low that the heterogeneity could not be
statistically distinguished from zero, we should be cautious in the
interpretation of a reduction in that estimate. Most likely, the
reduction in heterogeneity is better explained by imprecise estimation
than an actual explanation of unexplained heterogeneity.

Lastly, for two out of the 12 phenomena, the Albarracin_Priming_SAT and
the Shnabel_Willingness_Reconcile_Rev phenomena, we find
$\tau_{\sigma^2_X}$ of 0. Therefore, the $R_2$ metric could not be
computed, as the denominator would have been zero. However, we also did
not identify statistically significant ES heterogeneity in the first
place. The phenomena were assessed with a particularly low number of
replications (8 in both cases). Estimation precision for heterogeneity
in variance components, even more so than for ES, largely depends on the
sample size. Most likely, the low sample size led to implausible
estimates in both true and total score variance heterogeneity and
subsequently to an implausible estimate of $R_2$. Meta-analytic
estimates, especially those concerning score variance components such as
$R_2$, therefore should be interpreted with caution, if the sample size
was particularly low.
